%-------------------------     
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-0pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Large \scshape Jonathan Botros} \\ \vspace{1pt}
    \href{https://joneb.dev}{\underline{joneb.dev}} $|$
    \small  \href{mailto:jbotros7@gmail.com}{\underline{jbotros7@gmail.com}} $|$ 
    \href{https://linkedin.com/in/joneb}{\underline{linkedin.com/in/joneb}} $|$
    \href{https://github.com/jonebdev}{\underline{github.com/jonebdev}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New Jersey Institute of Technology}{Newark, NJ}
      {Bachelor of Arts in Computer Science}
      {September 2016 -- May 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    % \resumeSubheading
    %   {Undergraduate Research Assistant}{June 2020 -- Present}
    %   {Texas A\&M University}{College Station, TX}
    %   \resumeItemListStart
    %     \resumeItem{Developed a REST API using FastAPI and PostgreSQL to store data from learning management systems}
    %     \resumeItem{Developed a full-stack web application using Flask, React, PostgreSQL and Docker to analyze GitHub data}
    %     \resumeItem{Explored ways to visualize GitHub collaboration in a classroom setting}
    %   \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
% -------------------------------------------

    \resumeSubheading
      {Lead Full Stack Software Engineer}{April 2023 -- Present}
      {Kenvue (Formerly Known as Johnson \& Johnson Consumer Health)}{Skillman, NJ}
      \resumeItemListStart[leftmargin=0.15in]
        \resumeItem{Spearheaded development of Kenvue's Developer Portal built with Backstage.io, Typescript, React and Express.js, allowing 100+ teams to analyze and manage services, discover techincal documentation, and create new projects via templates. }
        \resumeItem{Launched 5+ Software Templates that include logging, linting, unit tests, and CI/CD pipelines. The template creation process includes integrations with tools like Sonarqube and Snyk, reducing the set up time from days to minutes.}
        \resumeItem{Migrated the developer portal from an EC2 to a Kubernetes cluster, establishing a DevSecOps Jenkins pipeline for multi-environment deployment via ArgoCD, reducing the release process from 1-2 hours to 10-15 minutes.}
        \resumeItem{Provided guidance and solution architecture for 3+ teams in the MarTech sector, ensuring adherence to best practices.}
        \resumeItem{Promoted the adoption of containerized static websites, resulting in the deployment of key brand websites with 1000+ visitors to a shared Kubernetes cluster, enhancing scalability, reducing costs, and increasing performance. }
    \resumeItemListEnd
    
    \resumeSubheading
      {Senior Full Stack Software Developer}{May 2022 -- March 2023}
      {Johnson \& Johnson}{Raritan, NJ}
      \resumeItemListStart[leftmargin=0.15in]
        \resumeItem{Engineered a React Native app for image labeling, accelerating the training of over 10 AI models for robotic surgery.}
        \resumeItem{Implemented CI/CD Jenkins pipeline for the mobile app web portal, which included unit tests, linting, static analysis, and deployment, boosting release efficiency by 40\% and incorporated best practices in code quality and deployment.}
        \resumeItem{Improved performance for the app's REST API. Removed 300 code smells, and increased unit test coverage by 50\%.}
        \resumeItem{Rewrote web portal using React, TypeScript, and Tailwind, improving data visualization and administrative functionality.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{June 2020 -- May 2022}
      {Johnson \& Johnson}{Raritan, NJ}
      \resumeItemListStart[leftmargin=0.15in]
        \resumeItem{Led backend PHP development for the Care4Today app which tracks patient symptoms, medication, and appointments. Created new trackers to generate risk scores, facilitating the onboarding of 100+ new clinical sites for research studies.}
        \resumeItem{Coached 3 other developers on the Care4Today backend team, enabling them to reduce tech debt by 30\% and increase unit tests by 10\% across the backend. Solved issues with Jenkins builds \& reviewed and debugged code with team.}
        \resumeItem{Architected serverless Node.js REST API for an mobile application to scan hashed bar codes stored in a PostgreSQL database for the Johnson \& Johnson Covid Vaccine, enabling lab workers to verify vaccine expiration status efficiently.}
        \resumeItem{Played key role in API strategy contributing to the Johnson \& Johnson API Catalog, which hosts over 150 APIs for internal discovery. Established CI/CD tools to streamline the upload of OpenAPI specifications to the API Catalog. }
      \resumeItemListEnd
        \resumeSubheading
      {Software Engineering Co-op}{June 2019 -- December 2019}
      {Johnson \& Johnson}{Raritan, NJ}
      \resumeItemListStart[leftmargin=0.15in]
        \resumeItem{Transitioned 10+ APIs in a critical API migration project from Apigee Trireme to Apigee Hosted Targets, documenting the migration process and supporting 4 overseas teams, successfully reaching internal deadlines ahead of schedule. }
        \resumeItem{Developed features for an internal developer companion application, built with Node.js \& React. The system provided a centralized source of data pooled from CI/CD tooling, resulting in valuable metrics for over 100+ J\&J projects.}
      \resumeItemListEnd

      \resumeSubheading
      {IT Intern}{May 2018 -- August 2018}
      {NJM Insurance}{West Trenton, NJ}
      \resumeItemListStart[leftmargin=0.15in]
        \resumeItem{Contributed to Selenium-based Automation Testing Tool using AngularJS, Java, and SQL, significantly improving automated QA testing experience for customer service tools, leading to 20\% less issues in new sign ups.}
      \resumeItemListEnd
  
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        % \resumeProjectHeading
        % {\textbf{joneb.dev} $|$ \emph{React, HTML, Javascript, Markdown}}{}
        % \resumeItemListStart[leftmargin=0.15in]
        %   \resumeItem{Personal site and blog created with Gatsby, React and TypeScript.}
        % \resumeItemListEnd
        % \resumeProjectHeading
        %   {\textbf{Playlist Converter} $|$ \emph{React, Node.js}   }
        %   {}
        %   \resumeItemListStart[leftmargin=0.15in]
        %     \resumeItem{Created website to migrate playlists between Spotify and Apple Music that integrated with both platforms' REST APIs.} 
        %   \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Youth Registration Form} $|$ \emph{React, Javascript}}{}
          \resumeItemListStart[leftmargin=0.15in]
            \resumeItem{Deployed new visitors card for a church youth group on the cloud, reducing waste and cutting costs by \$100 per year.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Color Fun Run} $|$ \emph{PHP, HTML, Javascript, MySQL}}{}
          \resumeItemListStart[leftmargin=0.15in]
            \resumeItem{Designed registration system for a color run with PHP, MySQL and HTML. The system integrated with Paypal's SDK and sent an email notifications upon new sign ups. The event had 180+ attendees and raised \$12,000.}
          \resumeItemListEnd  
        % \resumeItemListStart[leftmargin=0.15in]
        %   \resumeItem{\textbf{joneb.dev:} Personal website and blog created with Gatsby, React and TypeScript.}
        %   \resumeItem{\textbf{Playlist Converter:}  Web app that migrates playlists between Spotify and Apple Music that integrated with both platforms' REST APIs.}
        %   \resumeItem{\textbf{Youth Registration Form:}  Built a serverless registration form for a church youth group of 50 teenagers, reducing paper waste and cutting costs.}
        %   \resumeItem{\textbf{Color Fun Run:}  Created registration form for a charity event which integrated with the Paypal SDK and sent an email notification whenever someone registered. The event had 180+ attendees, and raised \$12,000 for clean water projects.}

        % \resumeItemListEnd
        
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
% \section{Projects}
%   \resumeItemListStart[leftmargin=0.15in]
%     \resumeItem{\textbf{joneb.dev:} Personal website and blog created with Gatsby, React and TypeScript.}
%     \resumeItem{\textbf{Playlist Converter:}  Web app that migrates playlists between Spotify and Apple Music that integrated with both platforms' REST APIs.}
%     \resumeItem{\textbf{Youth Registration Form:}  Built a serverless registration form for a church youth group of 50 teenagers, reducing paper waste and cutting costs.}
%     \resumeItem{\textbf{Color Fun Run:}  Created registration form for a charity event which integrated with the Paypal SDK and sent an email notification whenever someone registered. The event had 180+ attendees, and raised \$12,000 for clean water projects.}
%   \resumeItemListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Typescript, Javascript, Python, PHP, Bash, PostgreSQL, Java, HTML, CSS, Groovy, C++} \\
     \textbf{Frameworks and Libraries}{: React, Express.js, Next.js, React Native, FastAPI, Symfony, Knex.js, Backstage, Tailwind} \\
     \textbf{Developer Tools}{: Git, Docker, Kubernetes, Jenkins, Vite, AWS, Apigee, VSCode, Jenkins, Jira, Helm, Snyk, ArgoCD} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
